Explain urban regional function

### 2018-10-24 paper.tex
10-24

\documentclass{llncs}

\begin{document}

\title{Explain urban regional function}
\author{submission }
\maketitle
\section{Introduction}

%motivation
Urban computing importance ~\cite{1}
discovering regions of different functions~\cite{3} %3 references

%explain power
Previous model %
model complex, deep model
data heterogenous 
explainability -> disadvantage 
Explaining the result is of crucial importance

%explain implementation, we need to incorporate activity and online sentiment
Our goal is to label and cluster the region.
Furthermore, provide xxx explainations, activity , focus on aspects
activity
opinion
Example (figure)

%problem

segment regions = group regions with similar functions

@@

%contribution
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item According to what I have learnt,we are the first one to ap
  \item 2
  \item 3
\end{itemize}

%paper structure
The structure of our paper is listed as follow.Some previous work of former scholars are listed in Section 2.

%Problem and Objective.Methods and Model.Contributions and Findings

%paper structure
The remainder of the paper is organized as follows. 
We give an overview for related work in Section 2.
In Section 3, we introduce our novel models as well as proving their logic.
Section 4 presents the suprior result in experiments of our models.
Finally, we made a conclusion and looked forward to our future work in Section 5.

@@

%related work section name, find another suitable name for mobility mining
\subsection{Urban Computing}
%
Urban computing~\cite{1} tackles the major issues that cities face by analyzing human mobility collected from different sensors.  
Major sources of human mobility data are checkins in POI~\cite{}, pick-up and drop-off behavior of taxicabs~\cite{} in different locations and  trajectories~\cite{}.
%extract the different among these data
For checkins data, the most commonly adopted model is.
For taxicabs data, to fully utilize pick-up and drop-off, xxx is adopted to enhance xxx
For trajectory data, as it involves multiple points

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}

\begin{document}
\title{Explain urban regional function}
\author{Submission}

\maketitle

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Explanation  \and Urban computing \and Sentiment analysis.}
\end{abstract}
%

\section{Introduction}

\subsection{motivation}
Urban computing is defined by Zheng et al. ~\cite{Zheng2014UrbanConcepts} as an concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system.The aims of urban computing include improve the life level of residents,optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
With the improvement of living life of urban residents,GPS-embedded taxi begin to play an important part of urban computing.And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al. ~\cite{Zheng2011taxicabs} detect the flaws in the existing urban planning of a city using the GPS trajectories of taxis traveling in the urban areas. Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories.Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
As you can see, Urban computing is closely linked with urban life.

Discovering regions of different function is a step towards urban computing.In this direction,Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
%~\cite{Yuan2012FunctionRegion}~\cite{Yuan2015FunctionRegion}:latent activity trajectories~\cite{Yuan2018FunctionRegion}

\subsection{explain power}
%Previous model
The approaches to explanation recommendation system was developing recently.At the early time,the fundamental methods of personal recommendation is recommendation systems with user-based and item-based. Resnick et al.\cite{Resnick1994UserBased} found user-based collaboration filtering recommendation system.The explanation is the similar neighbors whose interests and rates tend to be consistent with target user.Analogously,Sarwar et al. \cite{Sarwar2001ItemBased} proposed the recommendation with item-based could find the suitable items which has similar features with purchased items.

%model complex, deep model
Variants of these basic model constitute the majority of explanation recommendation systems.e.g.,Pazzani et al.\cite{Pazzani2007ContentBased}
As time going

%data heterogenous 
%explainability -> disadvantage

%Explaining the result is of crucial importance
We can see that early recommendation systems tend to base on intuition and full with common sense,which improve users' satisfaction easily. Now the explanation recommendation systems is developing with more accuracy , which generate more satisfying results.Nevertheless ,the complexity of models is increasing at the meantime,which covers the intuition of whole structure and weakens the persuasiveness of models.So the explanation is playing an important part in recommendation systems.%~\cite{{Zhang2018SIGIR}}
Majority of users trust and choice satisfaction were highly correlated with the reliability of the explanations for recommendations.Herlocker et al.~\cite{Herlocker2000Explanation}  do an investigation which shows that explanation facilities can improve the acceptance of recommendation systems.The following experiments,e.g.,by Ferwerda et al.~\cite{Ferwerda2012ContentCorrelate} has proven the conclusion.We aim to propose models to explain the destination why we recommend it more persuasively

%explain implementation, we need to incorporate activity and online sentiment
Our goal is to proposed a model to predict taxi destination and provide persuasive explanation for it.
%Furthermore, provide xxx explaination, activity , focus on aspects

\begin{figure}
    \centering
    \includegraphics[scale=0.25]{Structure.png}
    \caption{The general structure of our paper}
    %\label{fig:my_label}
\end{figure}

\subsection{problem}
For solve the problem,we face two challenges.One of it is...and the other is ...
segment regions = group regions with similar functions

@@

\subsection{contribution}
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item According to what I have learned,we are the first one to state-of-the-art
  \item 2
  \item 3
\end{itemize}

\subsection{paper structure}
The remainder of the paper is organized as follows. 
We give an overview for related work in Section 2.
In Section 3, we introduce our novel models as well as proving their logic.
Section 4 presents the suprior result in experiments of our models.
Finally, we made a conclusion and looked forward to our future work in Section 5.

@@

%related work section name, find another suitable name for mobility mining
\subsection{Urban Computing}

Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.  
Major sources of human mobility data are checkins in POI~\cite{}, pick-up and drop-off behavior of taxicabs~\cite{} in different locations and  trajectories~\cite{}.
%extract the different among these data
For checkins data, the most commonly adopted model is.
For taxicabs data, to fully utilize pick-up and drop-off, xxx is adopted to enhance xxx
For trajectory data, as it involves multiple points
